


        

        \section{Directed TwoSpect}
        \label{directed}

            TwoSpect improvements myself (to do).

            \subsection{Target, directed and all-sky search sensitivity}
            \label{tradeoffs}

                Targeted (known object) vs directed (region)vs all-sky (everything).

            \subsection{Enhancements enabled by directed searching}
            \label{directed_enhancements}

                Modifications for directed search.

        \section{Quantifying Directedness}
        \label{quant_directed}

            How big are the $X$ patterns in the $R$ surface on the modulation depth versus frequency plane?
These $X$-patterns follow the lines $df = f_{\textup{signal}} \pm (f - f_\textup{signal})$, intersecting at $f_\textup{signal}$.

We expect the $X$ pattern to be where the template touches a peak or trough in the time-frequency plane, with an $R$ proportional to the peak in a way that is as the relative power of that bin compared the power in the whole sinusoid. 
Since the template touches only once per period, the ratio would be $T_{\textup{coh}} / P_{\textup{signal}}$. For Scorpius X-1 ($P = 68023.8259$ s), that would lead to ratios of roughly $0.026 \approx 1/38$ for 1800 s SFTs, $0.01 \approx 1/81$ for 840 s SFTs, and $0.0053 \approx 1/189$ for 360 s SFTs.

Yet in practice, as exemplified by pulsar 40 in the Mock Data Challenge, which used 360 s SFTs, the difference between the peak (correct template) $R$-value and the $X$-pattern arms was only a factor of 1/2 to 1/3.
This suggests that the `touch-at-one-point' model is oversimplified, and there is significant overlap still.
There would be a shearing process as $df$ deviates further from the true modulation depth, governed by the frequency bin resolution, $1/T_\textup{coh}$. 
For pulsar 40, $df = 0.046$ Hz, the amplitude of this modulation depth was only about $B = \left(2 \pi \textup{asini} f / P \right) \times \textup{coh} \approx $ 16 bins, with a period of 189 bins.
We could estimate the fractional power in the arms to then be $2 \pi / \cos^{-1} ((B-1) / B)$, or roughly $1/18$ for pulsar 40.
Taking the arccosine of $(B-2)/B$ instead yields roughly $1/12$.
This is closer to the 1/2 to 1/3 ratios observed in the analyses that than 1/189 predicted naively, although a proper study would require a closer look at the generation of TwoSpect \textit{exact templates}.
Understanding the $X$ structure more fully could inform future methods for maximum likelihood estimation on the $R$ statistic plane or, more likely, on the pushed-forward $p-value$ plane.

            ADDITIONAL CONTENT
        
            Quantify how good the improvements are in directed TwoSpect. 

            Cite Feldman-Cousins confidence intervals paper~\cite{FeldmanCousins1998}.

            Cite Ethan's thesis~\cite{RomeroThesis} and our paper, maybe by using generation functions to make better TwoSpect statistics.

        \section{Scorpius X-1 and XTE J1751-305: Directed TwoSpect results}
        \label{directed_results}
 
            Preliminary results of a directed search (possibly simulation-only).

            We have a great deal of material here already, just need to pull from figures and commentary from the Sco X-1 wiki. Keith recommends paralleling the Sco X-1 paper.




        %---------------------------------

	%The following is an example of using the commands \textit{ref}
	%and \textit{label}. With these commands theorems, chapters,
	%sections and figurres can be labeld with names in the tex file
	%and then refered to by these names in later tex files. In
	%chapter~\ref{intro} we saw section~\ref{sample_section} or
	%theorem~\ref{sample_theorem}.

	%Lastly, here is how to include a figure. First generate an
	%encapsulated postscript file in xfig, adobe illustrator or
	%some other program. The specific commands are found in
	%\textit{chap2.tex}.

        %\begin{figure}[htb]
        %\centerline{ \epsfig{figure=sample.eps, 
        %height =  1.5 in}}
        %\caption{Sample Figure}
        %\label{sample_figure}
        %\end{figure}

