% This is an AMS-LaTeX v. 1.2 File.

\documentclass[leqno,twoside]{report}
%\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
%\usepackage{amsfonts}
\usepackage{amsxtra}     % Use various AMS packages
\usepackage{rac}                        % Use Rackham thesis macros
\usepackage{dbl12}
%\usepackage{srcltx}
\usepackage{epsfig}
\usepackage{verbatim}
%\usepackage{geometry}
%\usepackage{url}
%\usepackage[intoc]{nomencl}
%\usepackage[hyperpageref]{backref}
\usepackage[colorlinks,linkcolor=black,urlcolor=black,citecolor=black,breaklinks]{hyperref}
%\usepackage{doi}
%\usepackage{hypdvips}
\usepackage{breakurl}
%\usepackage[all]{hypcap}
\usepackage{cite}
\usepackage{graphicx}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Redefine margins and other page formatting

\setlength{\oddsidemargin}{0.5in}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Various theorem environments. All of the following have the same numbering
% system as theorem.

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{prop}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{question}[theorem]{Question}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{assumption}[theorem]{Assumption}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{notation}[theorem]{Notation}
\newtheorem{condition}[theorem]{Condition}
\newtheorem{example}[theorem]{Example}
\newtheorem{introduction}[theorem]{Introduction}

\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}
\include{header}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\numberwithin{theorem}{chapter}        % Numbers theorems "x.y" where x
                                        % is the section number, y is the
                                        % theorem number

%\renewcommand{\thetheorem}{\arabic{chapter}.\arabic{theorem}}

%\makeatletter                          % This sequence of commands will
%\let\c@equation\c@theorem              % incorporate equation numbering
%\makeatother                           % into the theorem numbering scheme

%\renewcommand{\theenumi}{(\roman{enumi})}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%This command creates a box marked ``To Do'' around text.
%To use type \todo{  insert text here  }.

\newcommand{\todo}[1]{\vspace{5 mm}\par \noindent
\marginpar{\textsc{ToDo}}
\framebox{\begin{minipage}[c]{0.95 \textwidth}
\tt #1 \end{minipage}}\vspace{5 mm}\par}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\bibliographystyle{plain}       % Set the bibliography style to AMS
                                % alphabetized. (Can use ``amsalpha'' or
                                % ``abbrv''instead.)

% Title page as required by Rackham dissertation guidelines




\titlepage{Directed searches for continuous gravitational waves from spinning neutron stars in binary systems }{Grant David Meadors}{Doctor of Philosophy}
{Physics} {2014}
{ Professor John Keith Riles, Chair \\
  Professor Fred C. Adams\\
  Professor Nuria Pilar Calvet\\
  Research Scientist Herold Richard Gustafson\\
  Professor Timothy A. McKay\\
  Professor Stephen C. Rand
 }


% Begin the front matter as required by Rackham dissertation guidelines

\initializefrontsections

\unnumberedpage{Frontispiece}
%\unnumberedpage
\copyrightpage{Grant David Meadors}
% Copyright page

\setcounter{page}{1}

% LIGO DCC-P1400102
\dedicationpage{
%(Space for a fancy dedication, such as the following) \\
To the tree of Life, which took stardust and evolved into us.\\
%(Maybe in Latin, or Greek?)\\
%Pro arbore Vitae, ex nube stellarum ad nos evolvit.
}

\startacknowledgementspage
% Acknowledgements page

%This author should give thanks far beyond a simple page. It is too soon to write something so important.

Thanks should go beyond a simple page. 
Lest I forget, here let me reflect on all the people without whom I would not have made it here. 
To my parents, Erin Ann Bridget O'Rourke-Meadors and Gregory David Meadors, and my brother, Patrick Thomas Meadors. 
My grandmother, Florenceann O'Rourke (n\'{e}e Williams), made Reed College, my undergraduate, possible. 
Ethan Obie Romero-Severson is ever a devoted friend: team science for four years and counting!
Keith Riles has been a dedicated and conscientious adviser: steady progress is how new science is born.
Dick Gustafson introduced me to the field in 2005 and has helped ever since.
Evan Goetz pioneered this kind of search, paving the way.
Best to my office-mates, Jax Sanders \& Santiago Caride, on their way soon!
Keita Kawabe is a concerted collaborator and experimenter.
Chris Messenger ever-patiently organized the data challenge.
Marco Cavaglia orchestrated the World Science Festival exhibition, with all its fun.
Mike Landry encouraged me to come for my sojourn at Hanford.
Sheila Dwyer and Sheon Chua, helped me see the squeezed light at the end of the beam tube.
Conor Mow-Lowry and Alexander Khalaidovski, were likewise great squeezer friends. 
Nicolas Smith-Lefebvre has been there in LIGO since I started.
Lisa Barsotti \& Matt Evans and Daniel Sigg made our whole quantum optics experiment possible.
Greg Mendell got me started on cluster computing.
Dale Ingram helped me lead my first public LIGO tours.
To my physics friends at Michigan, one of the most tight-knit cohorts, thank you too.
My gratitude especially to Michelle Adan, Matt Bales \& Amanda Boomer, Kevin Bergemann, Alex Burgers and Bo Zhang, for all having organized our Get-a-Job meetings to get over the final hurdles.
Epidemiology compatriots have made Ann Arbor my home: thanks to Meghan Milbrath, Ian Spicknall, Erin Shellman and Bryan Mayer -- everyone in Edit Club is a Doctor now!
Psychology teammates, Emily Bonem, Ali Earl, and Stephanie Carpenter, brought me through a long winter: good luck, loose seals.
Even the sky is not the limit for my Michigan Flyers instructor, Jayne.
And to my dear friends Aric Knuth of English and James Leija of the University Musical Society, who brought me in one Thanksgiving.
Thanks I give now again.
Read on -- for more still, named within, made this work a reality.

This dissertation bears LIGO Document number DCC-P1400102~\footnote{For further questions, please contact the author: \href{mailto:gmeadors@umich.edu}{gmeadors@umich.edu}}.

%{Put Acknowledgements here}


% Table of contents, list of figures, etc.
\tableofcontents
\listoffigures
\listoftables
\listofappendices


\startthechapters 
% The individual files for each of the chapters are put here.
% Save each chapter of your thesis to a seperate tex file
% and then use the \input command to include this file in your
% thesis.  For instance you can save a file to "intro.tex" and 
% then type \input{intro}". 

    % Be sure to add DOIs to references where possible, or URLS


\chapter{Introduction}
\label{intro} 
\input{intro}
\chapter{Gravitational Waves and LIGO}
\label{chap2}
\input{chap2}
% General relativity, history, mathematics
% Also include...
% Early phase camera work, explanation of LIGO and
% the summer of 2009 doing small projects, e.g. Omega scans
% and detector characterization with Rana, Mike and Keita
\chapter{Feedforward: Auxiliary MICH-PRC Subtraction}
\label{chap3}
\input{chap3}
% Feedforward (Auxiliary MICH-PRC Subtraction)
\chapter{Squeezing: Quantum Vacuum Phase Noise}
\label{chap4}
\input{chap4}
% Squeezing contributions
\chapter{TwoSpect: Search for a Simulated Scorpius X-1}
\label{chap5}
\input{chap5}
% Binary neutron star search in Scorpius X-1
\chapter{Directed TwoSpect: Scorpius X-1 and XTE J1751-305}
\label{chap6}
\input{chap6}
% Directed TwoSpect
\chapter{Outreach: Exhibit at the World Science Festival}
\label{chap7}
\input{chap7}
% World Science Festival exhibit
\chapter{Conclusion}
\label{conclusion}
\input{conclusion}
% Summary of all results


\startappendices
\chapter{Fields and curvature}
\label{appendix}
\input{appendix}
\chapter{Scorpius X-1 real data detection efficiency}
\label{appendix2}
\input{appendix2}
\chapter{Scorpius X-1 further preliminary upper limits and outliers}
\label{appendix3}
\input{appendix3}

%\bibliography{biblio}   % Use the BibTeX file ``biblio.bib''.
\bibliography{bibliography}

%Abstract Page

\startabstractpage
{Directed searches for continuous gravitational waves from spinning neutron stars in binary systems } {Grant David Meadors} {Chair: John Keith Riles}

Gravitational wave (GW) detectors should soon reveal the universe in a way unlike any existing kind of telescope. 
These waves, predicted by General Relativity, radiate from accelerating gravitational quadrupoles, such as black holes, neutron stars and the Big Bang. 
Indirect evidence for GW comes from the work of Hulse and Taylor; the Laser Interferometer Gravitational Wave Observatory (LIGO) and allies seek to observe GWs directly. 
In this thesis, I discuss the goals and history of the LIGO project and the theory and practice of its operation, including my contributions to the scientific collaboration in feedforward signal filtering, directed binary pulsar star searches, and scientific outreach and education to the next generation of young scientists. 
Filtering improves LIGO range in the last science run, S6, by 4.14\% (H1) and 3.60\% (L1). 
The directed binary search, most sensitive of 4 methods in simulated data, has set 95\% confidence upper limits (40 Hz to 2040 Hz) on GW strain in S6.




\end{document}

